### 2018-01-18 Chapters/Introduction.tex
Update on Overleaf.

\documentclass[12pt]{article}

\usepackage{natbib}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Essays in \\Computational Management Science}
\author{Marcelo Salhab Brogliato}

\begin{document}
\maketitle

\section{Introduction}

If anything good can ever be said about the second world war, it might be this: the war effort sparked a massive number of scientific fields.

@@

\subsection{Distributed financial ledgers}

@@

Iota is another cryptocurrency, but, instead of using a blockchain, it proposes the use a ``tangle' architecture', which is a different way to store the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. It needs a minimum of transactions per seconds in order to work properly.

@@

\subsection{Sparse Distributed Memory}

@@

\bibliographystyle{apa}
\bibliography{sample.bib}
\end{document}

>>>>

\chapter{Introduction}
\bigskip

\noindent If anything good can ever be said about the second world war, it might be this: the war effort sparked a massive number of scientific fields.

@@

\section{Distributed financial ledgers}

@@

Iota is another cryptocurrency, but, instead of using a blockchain, it proposes the use a ``tangle architecture'', which is a different way to store the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. It needs a minimum of transactions per seconds in order to work properly.

@@

\section{Artificial Intelligence}

@@
